---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

```

```{css}
body {
  background-color: #2F4858;
  font-family: Arial, Helvetica, sans-serif;
  padding: 90px;
}

h2 {
  font-weight: bold;
  text-align: center;
  color: #F4E3B2;
  font-size: 45px;
}

h3 {
  font-weight: bold;
  text-align: center;
  color: #F4E3B2;
  font-size: 25px;
}

p {
  text-align: center;
  color: #FFFFFF;
}


```

## Youtube Thumbnail Analysis

I am looking to analyse the obtained data from my google form to see whether certain features of a YouTube thumbnail will affect my likeliness to watch and the appeal of the YouTube video.

```{r}
# csv file from our collected data
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQgWXRc4PtTkTKUYpKXDiJ8YtAl3nF38Snr8_hTgKf9SDcGQgSm1K1S1CtGhefUlaaf5vu3mxhss4q0/pub?output=csv"

# read the csv file
logged_data <- read_csv(csv_file)

# rename variables in our data frame
latest_data <- logged_data %>%
  rename(video_type = 2,
         text_percentage = 3,
         image_percentage = 4,
         thumbnail_emotion = 5,
         interesting_details = 6,
         likeliness_to_watch = 7
         )

# extracting vectors from our data frames for txt percentage and img percentage
txt_percentage <- latest_data$text_percentage
img_percentage <- latest_data$image_percentage

# summary values for report (means of txt and img percentage)
mean_txt_percentage <- mean(txt_percentage) %>%
  round(1)
mean_img_percentage <- mean(img_percentage) %>%
  round(1)

# dynamic comments
comment_1 <- paste("From our data we find that the mean percentage of thumbnail covered by text is", mean_txt_percentage, "% and the mean percentage of thumbnail covered by images is", mean_img_percentage, "%.")

```

### Summary Values:
`r comment_1`

From the following information we can see that thumbnails typically contain a higher percentage of images than text.

### Bar Chart One:

Our first bar chart is used to determine if the genre of Youtube video will influence my likeliness to watch the video:

```{r}
# first bar chart
latest_data %>%
  ggplot() +
    geom_bar(aes(x = likeliness_to_watch, fill = video_type)) +
  labs(title = "Most likely to watch what type of Youtube Video?",
       subtitle = "seeing what type of video am I more likely to watch     based on thumbnail",
       x = "likeliness to watch (1 - 5)",
       y = "video ount")

```

From this bar chart, we can see that I am most likely to watch 'Entertainment' Youtube videos over gaming, music and educational videos. We can also see how I did not look at any sports or news YouTube videos when filling out my observations for YouTube thumbnails. 

### Bar Chart Two:

Our second bar chart is used to determine if the emotion displayed on the thumbnail is dependent on the Youtube video genre.

```{r}
# second bar chart
latest_data %>%
  ggplot() +
    geom_bar(aes(x = video_type, fill = thumbnail_emotion)) +
  labs(title = "Does emotion displayed on the thumbnail depend on the video type?",
       x = "youtube video genre",
       y = "video count")
```
From this second bar chart, we can see that educational videos typically show calm emotions in their thumbnails while entertainment mostly show happy/exciting emotions but occasionally contain dramatic thumbnails which is fitting for entertainment videos.

We can also see that music videos generally showcase a mix of emotions on the thumbnails. This is to be expected as music videos typically can be very emotional in different ways depending on the vibe of the song or the message the artist is trying to get across with their music and music video.

