---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

```

```{css}
body {
  background-color: #2F4858;
  font-family: Arial, Helvetica, sans-serif;
  padding: 90px;
}

h2 {
  font-weight: bold;
  text-align: center;
  color: #F4E3B2;
  font-size: 45px;
}

h3 {
  font-weight: bold;
  text-align: center;
  color: #F4E3B2;
  font-size: 25px;
}

p {
  text-align: center;
  color: #FFFFFF;
}


```

## Youtube Thumbnail Analysis

I am looking to analyse the obtained data from my google form to see whether certain features of a YouTube thumbnail will affect my likeliness to watch and the appeal of the YouTube video.

```{r}
# csv file from our collected data
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQgWXRc4PtTkTKUYpKXDiJ8YtAl3nF38Snr8_hTgKf9SDcGQgSm1K1S1CtGhefUlaaf5vu3mxhss4q0/pub?output=csv"

# read the csv file
logged_data <- read_csv(csv_file)

# rename variables in our data frame
latest_data <- logged_data %>%
  rename(video_type = 2,
         text_percentage = 3,
         image_percentage = 4,
         thumbnail_emotion = 5,
         interesting_details = 6,
         likeliness_to_watch = 7
         )

# extracting vectors from our data frames for txt percentage and img percentage
txt_percentage <- latest_data$text_percentage
img_percentage <- latest_data$image_percentage

# summary values for report (means of txt and img percentage)
mean_txt_percentage <- mean(txt_percentage)
mean_img_percentage <- mean(img_percentage)

# dynamic comments
comment_1 <- paste("From our data we find that the mean percentage of thumbnail covered by text is", mean_txt_percentage, "% and the mean percentage of thumbnail covered by images is", mean_img_percentage, "%.")

```

### Summary Values:
`r comment_1`

From the following information we can see that thumbnails typically contain a higher percentage of images than text.

### Bar Chart One:

Our first bar chart is used to determine if the genre of Youtube video will influence my likeliness to watch the video:

```{r}
# first bar chart
latest_data %>%
  ggplot() +
    geom_bar(aes(x = likeliness_to_watch, fill = video_type)) +
  labs(title = "Most likely to watch what type of Youtube Video?",
       subtitle = "seeing what type of video am I more likely to watch     based on thumbnail",
       x = "likeliness to watch (1 - 5)",
       y = "video ount")

```

### Bar Chart Two:

Our second bar chart is used to determine if the emotion displayed on the thumbnail is dependent on the Youtube video genre.

```{r}
# second bar chart
latest_data %>%
  ggplot() +
    geom_bar(aes(x = video_type, fill = thumbnail_emotion)) +
  labs(title = "Does emotion displayed on the thumbnail depend on the video type?",
       x = "youtube video genre",
       y = "video count")
```